---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# notestar-demo

<!-- badges: start -->
<!-- badges: end -->

Steps I used to make this demo.

1.  Create a new project in RStudio with git repository.

2.  Performed first git commit.

3.  `usethis::use_readme_rmd()` to start taking notes.

4.  `notestar::use_notestar()` and `notestar:::use_notestar_makefile()`

5.  Edited `index.Rmd`, `_targets.R` and `R/functions.R` to create some workflow
    items, including `data/sleepstudy.csv`.

6.  Created some entries and wrote them for the demo.

``` r
notestar::notebook_create_page(date = "2021-04-10", slug = "about-demo")
notestar::notebook_create_page(date = "2021-04-11", slug = "data-exploration")
notestar::notebook_create_page(date = "2021-04-12", slug = "models")
```

7.  Added a csl and bib file to `notebook/book/assets` and uncommented code in
    the `_targets.R` and `notebook/index.Rmd` to use these files.
    
8.  `targets::tar_make()` or the Build (Ctrl+B) shortcut in RStudio along the
    way.

9.  `notestar::notebook_browse()` to view the notebook.

10. commit files and create repository with `usethis::use_github()`


*** 

Here is how the data/modeling flow into the notebook entries and into the final
notebook.

```{r graph, dpi = 144}
targets::tar_visnetwork(targets_only = TRUE)
```

